A Comparative study of Dask and Spark for neuroimaging pipelines

### 2019-06-26 latex/paper.tex
Edited section Datasets

\subsubsection{Dask} Dask is a Big Data engine that is becoming
increasingly popular in the scientific Python ecosystem. \TG{A few more
introductory sentences should be added, following Spark's model.}
Dask represents application tasks as Dask graphs, produced by a
user-facing API and executed by a scheduler. We used the \href{https://distributed.dask.org/en/latest/index.html}{Dask
Distributed} scheduler.
Dask Distributed also has a LIFO policy. In theory, it should speed-up the
pipeline execution by finishing a branch of task computations before
starting new ones \TG{This is meant to reduce the memory footprint of the
application}. \TG{Here we should add a few comparison sentences between
Spark's and Dask's schedulers.} Dask has five main APIs: Dask Bags, Dask
Arrays, Dask Futures, Dask Delayed and DataFrames. We compared them all
except DataFrames as they are not adapted to the type of data we
considered. All APIs provide in-memory computing, data locality, and lazy
evaluation, however, none of them has fault tolerance \TG{Check fault
tolerance in Dask. Fine-grained lineage vs Spark's coarse grained lineage}.
We used Dask v1.1.4.

\href{https://docs.dask.org/en/latest/bag.html}{Dask Bags}
are parallel collections of Python objects, similar to Spark's RDD. Dask
Bags also offers optimized algorithms \TG{``optimized algorithms'' is
inaccurate: you should explain what they do} that mimic most of the
toolz~\cite{toolz} library. \href{https://docs.dask.org/en/latest/array.html}{Dask
Arrays} are used for the
processing of large arrays. They provide a parallel clone of the popular
NumPy library. \href{https://docs.dask.org/en/latest/delayed.html}{Dask
Delayed} supports arbitrary
tasks that does not fit in the Array, DataFrame or MapReduce \TG{Do you
mean Bags?} frameworks. Finally, \href{https://docs.dask.org/en/latest/futures.html}{Dask
Futures} is similar to Dask
Delayed as it supports arbitrary tasks, but it operates in real-time rather
than lazily.

\subsection{Dataset}
For the incrementation and histogram experiment, the BigBrain~\cite{Amunts:13} is
used. It is a three-dimensional image of a brain scanned at \SI{40}{\micro\metre}.
The dataset stores the intensity of each voxel and its position. This results in a
75GB image. It is stored in 125 chunks in the \textit{MINC}~\cite{minc} format. To
perform our experiment we convert the chunks into the \textit{NifTI}~\cite{nifti}
format. Also, using \textit{sam}~\cite{sam} we combine the chunks and split them into
30, 125 and 750 chunks of equal size; each of 2.5GB, 0.6GB, and 0.1GB, respectively.

\subsection{Applications}
%% Incrementation
\subsubsection{\textbf{Incrementation}}
As our first experiment to benchmark the frameworks, we used a simple incrementation
pipeline (see Algorithm~\ref{alg:incrementation}). It reads chunks from the BigBrain
image, increments the intensity value of each voxel by 1 for a specified amount of
iterations, and writes the result to an NFS as a NifTI image. Incrementing the data
reduce the caching effect. This experiment allows us to study the behavior of the
frameworks when all inputs are processed independently; i.e.\ each task in the graph
only depends on the previous one (see Figure~\ref{fig:tg-inc}). This mimics the
behavior of analyzing multiple independent subjects in parallel.

@@

\begin{algorithm}[!b]
    \caption{Incrementation}\label{alg:incrementation}
    \begin{algorithmic}
    \Require{\(x\), a sleep delay in float}
    \Require{\(file\), a file containing a chunk}
    \Require{\(fs\), NFS to write image to.}
    \State{Read \(chunk\) from \(file\)}
    \ForEach{\(i \in iterations\)}
        \ForEach{\(chunk \in image\)}
            \State{\(chunk\gets chunk+1\)}
            \State{Sleep \(x\)}
        \EndFor
    \EndFor
    \State{Write \(chunk\) to \(fs\)}
\end{algorithmic}
\end{algorithm}

@@

\begin{algorithm}[!t]
    \caption{Histogram}\label{alg:histogram}
    \begin{algorithmic}
    \Require{\(files\), files containing BigBrain}
    \Require{\(fs\), NFS to save image to.}
    \ForEach{\(file \in files\)}
        \State{Read \(chunk\) from \(file\)}
        \State{{Calculate \(frequency\) of \(chunks\)}}
    \EndFor

@@

\textbf{Number of chunks:} Evaluating the frameworks on a different amount of chunks
allows us to understand their behavior with different task size and IO requirements.

@@

The baseline for our experiments is: 8 workers, 125 chunks, 10 iterations and 4
seconds sleep delay.

\begin{table}[!t]
    \renewcommand{\arraystretch}{1.3}
    \caption{Parameters for the experiments}\label{tab:param}
    \centering
    \begin{tabular*}{\columnwidth}{llll}
    \hline
                        & Incrementation & Histogram             & BIDS Example          \\ \hline
    \# of worker        & 1, 2, 4, 8     & 1, 2, 4, 8            & 1, 2, 4, 8            \\
    \# of chunks        & 30, 125, 750   & 30, 125, 750          & 30, 125, 750          \\
    \# of iterations    & 1, 10, 100     & \multicolumn{1}{c}{-} & \multicolumn{1}{c}{-} \\
    Sleep delay {[}s{]} & 1, 4, 16, 64   & \multicolumn{1}{c}{-} & \multicolumn{1}{c}{-} \\ \hline
    \end{tabular*}
    \end{table}

@@

\begin{figure}[!b]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/inc_worker.png}%
        \caption{Incrementation makespan}\label{fig:inc_ms_worker}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/inc_idle_worker.png}%
        \caption{Incrementation total time}\label{fig:inc_tt_worker}
    \end{subfigure}
    \caption{125 chunks, 10 iterations, 4 sec.\ sleep delay}\label{fig:inc_worker}
\end{figure}

% Chunks
\subsection{Experiment 1: Number of chunks}
In Figure~\ref{fig:inc_chunk}, Spark is not compared for 30 chunks. This is because
Spark has a 2GB limitation in the task size it can compute.

The Figure~\ref{fig:inc_ms_chunk} shows the makespan evolution when varying the
number of chunks. The compute time increase when there are more chunks. This is
because the sleep delay is constant throughout this experiment and there are more
compute tasks when the number of chunks increases.

In Figure~\ref{fig:inc_tt_chunk}, the total execution time of each function is shown.
For 30 chunks the Dask Bag API has a much lower overhead time. This is because we
only calculate the idle time of the used core. Dask Bag was only using one thread per
block in comparison to Dask Delayed and Dask Futures which was offloading a block
calculations on multiple threads of the same worker. Furthermore, the variance of the
overhead increases proportionally to the number of chunks. Also, the IO time reduces
with more chunks however the overhead time increase by a similar amount. This is not
observed for 30 chunks as the workers are not used at full capacity; i.e.\ some
threads are idle.

\begin{figure}[!t]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/inc_chunk.png}%
        \caption{Incrementation makespan}\label{fig:inc_ms_chunk}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/inc_idle_chunk.png}%
        \caption{Incrementation total time}\label{fig:inc_tt_chunk}
    \end{subfigure}
    \caption{10 iterations, 4 sec.\ sleep delay, 8 instances}\label{fig:inc_chunk}
\end{figure}

@@

\begin{figure}[!t]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/inc_itr.png}%
        \caption{Incrementation makespan}\label{fig:inc_ms_itr}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/inc_idle_itr.png}%
        \caption{Incrementation total time}\label{fig:inc_tt_itr}
    \end{subfigure}
    \caption{125 chunks, 4 sec.\ sleep delay, 8 instances}
\end{figure}

@@

\begin{figure}[!t]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/inc_sleep.png}%
        \caption{Incrementation makespan}\label{fig:inc_ms_sleep}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/inc_idle_sleep.png}%
        \caption{Incrementation total time}\label{fig:inc_tt_sleep}
    \end{subfigure}
    \caption{125 chunks, 10 iterations, 8 instances}
\end{figure}

@@

\begin{figure*}[!htb]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/spark_inc_baseline_gantt.png}
        \caption{Spark execution timeline}\label{fig:inc_spark_gantt}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/Dask_bag_inc_baseline_gantt.png}%
        \caption{Dask Bag execution timeline}\label{fig:inc_dask_bag_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/Dask_delayed_inc_baseline_gantt.png}%
        \caption{Dask Delayed execution timeline}\label{fig:inc_dask_delayed_gantt}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/Dask_futures_inc_baseline_gantt.png}%
        \caption{Dask Futures execution timeline}\label{fig:inc_dask_futures_gantt}
    \end{subfigure}
    \caption{125 chunks, 4 sec.\ sleep delay, 8 instances}\label{fig:inc_gantt}
\end{figure*}

% \begin{table}[!b]
%     \renewcommand{\arraystretch}{1.3}
%     \caption{Distribution of the execution time in second: 125 chunks, 4 sec.\ sleep
%     delay, 10 iterations, and 8 workers}\label{tab:inc_base}
%     \centering
%     \begin{tabular*}{\columnwidth}{llllll}
%     \hline
%                  & Read  & Compute & Write & Overhead & Total \\ \hline
%     Spark        & 34465 & 5118    & 22679 & 17076    & 79338 \\
%     Dask Bag     & 36863 & 5121    & 15449 & 21388    & 78821 \\
%     Dask Delayed & 32769 & 5119    & 11373 & 26199    & 75461 \\
%     Dask Futures & 31891 & 5120    & 11270 & 27984    & 76265 \\ \hline
%     \end{tabular*}
%  \end{table}

@@

\begin{figure}[!t]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/histo_instance.png}%
        \caption{Histogram makespan}\label{fig:histo_ms_worker}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/histo_idle_instances.png}%
        \caption{Histogram total time}\label{fig:histo_tt_worker}
    \end{subfigure}
    \caption{125 chunks}
\end{figure}

\subsection{Experiment 2: Number of chunks}

\begin{figure}[!t]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/histo_splits.png}%
        \caption{Histogram makespan}\label{fig:histo_ms_chunk}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/histo_idle_splits.png}%
        \caption{Histogram total time}\label{fig:histo_tt_chunk}
    \end{subfigure}
    \caption{8 workers}
\end{figure}

@@

\subsection{Caching}
We think that caching plays an effect on the results. As seen in the Gantt chart
previously, some of the read tasks are significantly shorter than others while all
chunks are of equal size.

>>>>

\subsubsection{Dask} Dask is a Big Data engine that is becoming
increasingly popular in the scientific Python ecosystem. \TG{A few more
introductory sentences should be added, following Spark's model.}
Dask represents application tasks as Dask graphs, produced by a
user-facing API and executed by a scheduler. We used the \href{https://distributed.dask.org/en/latest/index.html}{Dask
Distributed} scheduler.
Dask Distributed also has a LIFO policy. In theory, it should speed-up the
pipeline execution by finishing a branch of task computations before
starting new ones \TG{This is meant to reduce the memory footprint of the
application}. \TG{Here we should add a few comparison sentences between
Spark's and Dask's schedulers.} Dask has five main APIs and data structures: Bag,
Array, Futures, Delayed and DataFrame. We used them all
except DataFrame as it is not adapted to the type of data we
used. All APIs provide in-memory computing, data locality, and lazy
evaluation, however, none of them has fault tolerance \TG{Check fault
tolerance in Dask. Fine-grained lineage vs Spark's coarse grained lineage}.
We used Dask v1.1.4.

In Dask, a \href{https://docs.dask.org/en/latest/bag.html}{Bag} is a parallel
collection of Python objects, similar to Spark's RDD. It offers a
programming abstraction similar to the
\href{https://toolz.readthedocs.io/en/latest/}{PyToolz library}.
An \href{https://docs.dask.org/en/latest/array.html}{Array} is used for
the processing of large arrays. It provides a distributed clone of the
popular
NumPy library. \href{https://docs.dask.org/en/latest/delayed.html}{Delayed} supports arbitrary
tasks that do not fit in the Array, DataFrame or Bag frameworks. 
Finally, \href{https://docs.dask.org/en/latest/futures.html}{Futures} are similar to
Delayed as they support arbitrary tasks, but they operate in real-time rather
than lazily.

\subsection{Dataset}

We used BigBrain~\cite{Amunts:13}, a three-dimensional image of a human
brain. The original data is stored in 125 blocks in the MINC~\cite{minc}
HDF5-based format, available at
\url{ftp://bigbrain.loris.ca/BigBrainRelease.2015/3D_Blocks/40um} at the
resolution of \SI{40}{\micro\metre}. We converted the blocks into the
\href{https://nifti.nimh.nih.gov/nifti-1}{NifTI} format, a popular format
in neuroimaging. We left the NifTI blocks uncompressed, resulting in 
a total data size of 76~GiB \TG{Check if GiB or GB}. 
To evaluate the effect of block size, we resplit these blocks into 30, 125 and 750 blocks of 
2.5GB, 0.6GB, and
0.1GB \TG{check sizes}, using the sam~\cite{sam} library.

We also used the dataset provided by the Consortium for Reliability and
Reproducibility
(\href{http://fcon_1000.projects.nitrc.org/indi/CoRR/html/}{CoRR}) as
available on
\href{http://datasets.datalad.org/?dir=/corr/RawDataBIDS}{DataLad}. The
entire dataset is 408.4~GB, containing anatomical, diffusion and functional
images of 1,397 subjects acquired in 29 sites. Among these, we only used
data from \TG{X} subjects, representing \TG{Y}GB overall (\TG{Z}GB by
subject on average).

\subsection{Applications}
%% Incrementation
\subsubsection{\textbf{Incrementation}}
As our first experiment to benchmark the frameworks, we used a simple incrementation
pipeline (see Algorithm~\ref{alg:incrementation}). It reads blocks from the BigBrain
image, increments the intensity value of each voxel by 1 for a specified amount of
iterations, and writes the result to an NFS as a NifTI image. Incrementing the data
reduce the caching effect. This experiment allows us to study the behavior of the
frameworks when all inputs are processed independently; i.e.\ each task in the graph
only depends on the previous one (see Figure~\ref{fig:tg-inc}). This mimics the
behavior of analyzing multiple independent subjects in parallel.

@@

\begin{algorithm}[!b]
    \caption{Incrementation}\label{alg:incrementation}
    \begin{algorithmic}
    \Require{\(x\), a sleep delay in float}
    \Require{\(file\), a file containing a block}
    \Require{\(fs\), NFS to write image to.}
    \State{Read \(block\) from \(file\)}
    \ForEach{\(i \in iterations\)}
        \ForEach{\(block \in image\)}
            \State{\(block\gets block+1\)}
            \State{Sleep \(x\)}
        \EndFor
    \EndFor
    \State{Write \(block\) to \(fs\)}
\end{algorithmic}
\end{algorithm}

@@

\begin{algorithm}[!t]
    \caption{Histogram}\label{alg:histogram}
    \begin{algorithmic}
    \Require{\(files\), files containing BigBrain}
    \Require{\(fs\), NFS to save image to.}
    \ForEach{\(file \in files\)}
        \State{Read \(block\) from \(file\)}
        \State{{Calculate \(frequency\) of \(blocks\)}}
    \EndFor

@@

\textbf{Number of blocks:} Evaluating the frameworks on a different amount of blocks
allows us to understand their behavior with different task size and IO requirements.

@@

The baseline for our experiments is: 8 workers, 125 blocks, 10 iterations and 4
seconds sleep delay.

\begin{table}[!t]
    \renewcommand{\arraystretch}{1.3}
    \caption{Parameters for the experiments}\label{tab:param}
    \centering
    \begin{tabular*}{\columnwidth}{llll}
    \hline
                        & Incrementation & Histogram             & BIDS Example          \\ \hline
    \# of worker        & 1, 2, 4, 8     & 1, 2, 4, 8            & 1, 2, 4, 8            \\
    \# of blocks        & 30, 125, 750   & 30, 125, 750          & 30, 125, 750          \\
    \# of iterations    & 1, 10, 100     & \multicolumn{1}{c}{-} & \multicolumn{1}{c}{-} \\
    Sleep delay {[}s{]} & 1, 4, 16, 64   & \multicolumn{1}{c}{-} & \multicolumn{1}{c}{-} \\ \hline
    \end{tabular*}
    \end{table}

@@

\begin{figure}[!b]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/inc_worker.png}%
        \caption{Incrementation makespan}\label{fig:inc_ms_worker}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/inc_idle_worker.png}%
        \caption{Incrementation total time}\label{fig:inc_tt_worker}
    \end{subfigure}
    \caption{125 blocks, 10 iterations, 4 sec.\ sleep delay}\label{fig:inc_worker}
\end{figure}

% blocks
\subsection{Experiment 1: Number of blocks}
In Figure~\ref{fig:inc_block}, Spark is not compared for 30 blocks. This is because
Spark has a 2GB limitation in the task size it can compute.

The Figure~\ref{fig:inc_ms_block} shows the makespan evolution when varying the
number of blocks. The compute time increase when there are more blocks. This is
because the sleep delay is constant throughout this experiment and there are more
compute tasks when the number of blocks increases.

In Figure~\ref{fig:inc_tt_block}, the total execution time of each function is shown.
For 30 blocks the Dask Bag API has a much lower overhead time. This is because we
only calculate the idle time of the used core. Dask Bag was only using one thread per
block in comparison to Dask Delayed and Dask Futures which was offloading a block
calculations on multiple threads of the same worker. Furthermore, the variance of the
overhead increases proportionally to the number of blocks. Also, the IO time reduces
with more blocks however the overhead time increase by a similar amount. This is not
observed for 30 blocks as the workers are not used at full capacity; i.e.\ some
threads are idle.

\begin{figure}[!t]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/inc_block.png}%
        \caption{Incrementation makespan}\label{fig:inc_ms_block}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/inc_idle_block.png}%
        \caption{Incrementation total time}\label{fig:inc_tt_block}
    \end{subfigure}
    \caption{10 iterations, 4 sec.\ sleep delay, 8 instances}\label{fig:inc_block}
\end{figure}

@@

\begin{figure}[!t]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/inc_itr.png}%
        \caption{Incrementation makespan}\label{fig:inc_ms_itr}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/inc_idle_itr.png}%
        \caption{Incrementation total time}\label{fig:inc_tt_itr}
    \end{subfigure}
    \caption{125 blocks, 4 sec.\ sleep delay, 8 instances}
\end{figure}

@@

\begin{figure}[!t]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/inc_sleep.png}%
        \caption{Incrementation makespan}\label{fig:inc_ms_sleep}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/inc_idle_sleep.png}%
        \caption{Incrementation total time}\label{fig:inc_tt_sleep}
    \end{subfigure}
    \caption{125 blocks, 10 iterations, 8 instances}
\end{figure}

@@

\begin{figure*}[!htb]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/spark_inc_baseline_gantt.png}
        \caption{Spark execution timeline}\label{fig:inc_spark_gantt}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/Dask_bag_inc_baseline_gantt.png}%
        \caption{Dask Bag execution timeline}\label{fig:inc_dask_bag_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/Dask_delayed_inc_baseline_gantt.png}%
        \caption{Dask Delayed execution timeline}\label{fig:inc_dask_delayed_gantt}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/Dask_futures_inc_baseline_gantt.png}%
        \caption{Dask Futures execution timeline}\label{fig:inc_dask_futures_gantt}
    \end{subfigure}
    \caption{125 blocks, 4 sec.\ sleep delay, 8 instances}\label{fig:inc_gantt}
\end{figure*}

% \begin{table}[!b]
%     \renewcommand{\arraystretch}{1.3}
%     \caption{Distribution of the execution time in second: 125 blocks, 4 sec.\ sleep
%     delay, 10 iterations, and 8 workers}\label{tab:inc_base}
%     \centering
%     \begin{tabular*}{\columnwidth}{llllll}
%     \hline
%                  & Read  & Compute & Write & Overhead & Total \\ \hline
%     Spark        & 34465 & 5118    & 22679 & 17076    & 79338 \\
%     Dask Bag     & 36863 & 5121    & 15449 & 21388    & 78821 \\
%     Dask Delayed & 32769 & 5119    & 11373 & 26199    & 75461 \\
%     Dask Futures & 31891 & 5120    & 11270 & 27984    & 76265 \\ \hline
%     \end{tabular*}
%  \end{table}

@@

\begin{figure}[!t]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/histo_instance.png}%
        \caption{Histogram makespan}\label{fig:histo_ms_worker}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/histo_idle_instances.png}%
        \caption{Histogram total time}\label{fig:histo_tt_worker}
    \end{subfigure}
    \caption{125 blocks}
\end{figure}

\subsection{Experiment 2: Number of blocks}

\begin{figure}[!t]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/histo_splits.png}%
        \caption{Histogram makespan}\label{fig:histo_ms_block}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/histo_idle_splits.png}%
        \caption{Histogram total time}\label{fig:histo_tt_block}
    \end{subfigure}
    \caption{8 workers}
\end{figure}

@@

\subsection{Caching}
We think that caching plays an effect on the results. As seen in the Gantt chart
previously, some of the read tasks are significantly shorter than others while all
blocks are of equal size.
